Distinction Centrality Analysis

### 2025-07-20 analysis.qmd
just do it

## Connected Caves Computational Experiments
```{r}
   source(here("Functions", "connect.caves.R"))
   source(here("Functions", "gg2.R"))
   set.seed(456)
   b <- connect.caves(c = 4, nc = 4, n = 24)
   p.list <- lapply(b, gg2, lay.o = "auto")
   for (i in 1:length(p.list)) {
      p.list[[i]] <- p.list[[i]] + ggtitle(paste("N. Long Ties =", i-1)) +
         theme(plot.title = element_text(size = 11))
      }
   wrap_plots(p.list[c(1:4)], nrow = 2)
   ggsave(here("Plots", "connected-caves-examples1.png"), width = 10, height = 10, units = "in")
   wrap_plots(p.list[c(5:8)], nrow = 2)
   ggsave(here("Plots", "connected-caves-examples2.png"), width = 10, height = 10, units = "in")
   wrap_plots(p.list[c(9:12)], nrow = 2)
   ggsave(here("Plots", "connected-caves-examples3.png"), width = 10, height = 10, units = "in")
   wrap_plots(p.list[c(13:16)], nrow = 2)
   ggsave(here("Plots", "connected-caves-examples4.png"), width = 10, height = 10, units = "in")
```

## Broker Computational Experiements

>>>>

## Star Graph Computational Experiments

```{r}
   make.stars <- function(n = 30) {
      gl <- vector(mode = "list", length = n)
      gl[[1]] <- make_star(3, mode = "undirected") 
      for (k in 2:n) {
         gl[[k]] <- make_star(k+2, mode = "undirected") 
         }
      return(gl)
      }
   b <- make.stars(33)
   c <- lapply(b, distinction)
   ds.s <- sapply(c, function(x) {x[1, 3]})
   ds.p <- sapply(c, function(x) {x[2, 3]})
   d.s <- sapply(c, function(x) {x[1, 2]})
   d.p <- sapply(c, function(x) {x[2, 2]})
   dat <- data.frame(d = c(ds.s, ds.p, d.s, d.p), 
         n = c(1:length(d.s), 1:length(d.s), 1:length(d.s), 1:length(d.s)),
         g = c(rep(1, length(d.s)), rep(2, length(d.s)), 
         rep(3, length(d.s)), rep(4, length(d.s)))) |> 
         mutate(g = factor(g, labels = c(
                           "Scaled Distinction (Star)", 
                           "Scaled Distinction (Peripheral)", 
                           "Non-scaled Distinction (Star)",
                           "Non-scaled Distinction (Peripheral)"))) |> 
         mutate(n = n + 2)
   p <- ggplot(dat, aes(n, d, group = g, color = as.factor(g))) 
   p <- p + geom_point(size = 3)
   p <- p + geom_line(linewidth = 0.75)
   p <- p + geom_hline(yintercept = 0, color = "red", linetype = 2)
   p <- p + labs(y = "", x = "Star Size")
   p <- p + scale_x_continuous(breaks = seq(3, length(d.s), by = 3))
   p <- p + scale_color_manual(values = c("red", "blue", "tan2", "purple"))
   p <- p + theme_minimal()
   p <- p + theme(axis.text = element_text(size = 14, face = "bold"),
                  axis.title = element_text(size = 16, face = "bold"),
                  legend.text = element_text(size = 16, face = "bold"),
                  legend.title = element_blank(),
                  legend.position = "top"
                  )
   p <- p + guides(color = guide_legend(nrow = 2))
   p
   ggsave(here("Plots", "star-roles-by-size.png"), width = 7, height = 7, units = "in")
```
## Connected Caves Computational Experiments
```{r}
   source(here("Functions", "connect.caves.R"))
   source(here("Functions", "gg2.R"))
   set.seed(456)
   b <- connect.caves(c = 4, nc = 4, n = 24)
   p.list <- lapply(b, gg2, lay.o = "auto")
   for (i in 1:length(p.list)) {
      p.list[[i]] <- p.list[[i]] + ggtitle(paste("N. Long Ties =", i-1)) +
         theme(plot.title = element_text(size = 11))
      }
   wrap_plots(p.list[c(1:4)], nrow = 2)
   ggsave(here("Plots", "connected-caves-examples1.png"), width = 10, height = 10, units = "in")
   wrap_plots(p.list[c(5:8)], nrow = 2)
   ggsave(here("Plots", "connected-caves-examples2.png"), width = 10, height = 10, units = "in")
   wrap_plots(p.list[c(9:12)], nrow = 2)
   ggsave(here("Plots", "connected-caves-examples3.png"), width = 10, height = 10, units = "in")
   wrap_plots(p.list[c(13:16)], nrow = 2)
   ggsave(here("Plots", "connected-caves-examples4.png"), width = 10, height = 10, units = "in")
```

## Broker Computational Experiments
